A full approximation storage multilevel method \\ for nonlinear variational inequalities

### 2022-12-28 paper/fascd.tex
a few replacements

FIXME show results for 2D Firedrake implementation of NMCD for $p$-Laplacian obstacle problem (Example \ref{ex:plaplacian}), advection-diffusion obstacle problem (Example \ref{ex:advectiondiffusion}), and porous-media obstacle problem (Example \ref{ex:porous})

@@

FIXME in Appendix we show how NMCD reduces to FAS if the obstacle is removed and to MCD if $f$ is assumed to be linear

@@

\appendix
\section{Reductions of NMCD to familiar multilevel algorithms} \label{app:reductions}

Algorithm \ref{alg:fascd} in the main text, \pr{nmcd-vcycle}, generalizes two better-known multilevel algorithms.  First we show that it reduces to the FAS multigrid V-cycle for nonlinear PDEs (which itself generalizes the standard linear multigrid V-cycle \cite{Trottenbergetal2001}).  Second we reduce NMCD to an existing MCD V-cycle for unilateral linear variational inequalities \cite{GraeserKornhuber2009}.  This Appendix helps readers understand Algorithm \ref{alg:fascd} by separating those assumptions which relate to nonlinear and FAS aspects from the nontrivial modifications of standard multigrid which are caused by inequality constraints.  The later arise even when $f$ in \eqref{eq:vi} is a linear operator.

@@

\begin{pseudofloat}[ht]
\begin{pseudo} \label{ps:fas-vcycle}
\pr{fas-vcycle}(\ell^J; w^J)\text{:} \\+
    for $j=J$ downto $j=1$ \\+
      $\text{\pr{smooth}}^{\text{\id{down}}}(\ell^j;w^j)$ \\
      $w^{j-1} = \iR w^j$ \\
      $\ell^{j-1} = f^{j-1}(w^{j-1}) + R \left(\ell^j - f^j(w^j)\right)$ \\-
    $\text{\pr{solve}}(\ell^0;w^0)$ \\
    for $j=1$ to $j=J$ \\+
      $w^j \gets w^j + P (w^{j-1} - \iR w^j)$ \\
      $\text{\pr{smooth}}^{\text{\id{up}}}(\ell^j;w^j)$ \\-
\end{pseudo}
\caption{An FAS V-cycle results from removing the inequality constraints from \pr{nmcd-vcycle}, and simplifying accordingly.}
\label{alg:fas}
\end{pseudofloat}

>>>>

FIXME show results for 2D Firedrake implementation of FASCD for $p$-Laplacian obstacle problem (Example \ref{ex:plaplacian}), advection-diffusion obstacle problem (Example \ref{ex:advectiondiffusion}), and porous-media obstacle problem (Example \ref{ex:porous})

@@

@@

\appendix
\section{Reductions of FASCD to familiar multilevel algorithms} \label{app:reductions}

Algorithm \ref{alg:fascd} in the main text, \pr{fascd-vcycle}, generalizes two better-known multilevel algorithms.  First we show that it reduces to the FAS multigrid V-cycle for nonlinear PDEs (which itself generalizes the standard linear multigrid V-cycle \cite{Trottenbergetal2001}).  Second we reduce FASCD to an existing MCD V-cycle for unilateral linear variational inequalities \cite{GraeserKornhuber2009}.  This Appendix helps readers understand Algorithm \ref{alg:fascd} by separating those assumptions which relate to nonlinear and FAS aspects from the nontrivial modifications of standard multigrid which are caused by inequality constraints.  The later arise even when $f$ in \eqref{eq:vi} is a linear operator.

@@

\begin{pseudofloat}[ht]
\begin{pseudo} \label{ps:fas-vcycle}
\pr{fas-vcycle}(\ell^J; w^J)\text{:} \\+
    for $j=J$ downto $j=1$ \\+
      $\text{\pr{smooth}}^{\text{\id{down}}}(\ell^j;w^j)$ \\
      $w^{j-1} = \iR w^j$ \\
      $\ell^{j-1} = f^{j-1}(w^{j-1}) + R \left(\ell^j - f^j(w^j)\right)$ \\-
    $\text{\pr{solve}}(\ell^0;w^0)$ \\
    for $j=1$ to $j=J$ \\+
      $w^j \gets w^j + P (w^{j-1} - \iR w^j)$ \\
      $\text{\pr{smooth}}^{\text{\id{up}}}(\ell^j;w^j)$ \\-
\end{pseudo}
\caption{An FAS V-cycle results from removing the inequality constraints from \pr{fascd-vcycle}, and simplifying accordingly.}
\label{alg:fas}
\end{pseudofloat}
